---
title: "Avocado Price Data Visualization"
author: "B10401038"
date: "2018?~10??3??"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Data Content
source:https://www.kaggle.com/neuromusic/avocado-prices

*** 

This data was downloaded from the [Hass Avocado Board website](http://www.hassavocadoboard.com) in May of 2018 & compiled into a single CSV. 

The table below represents weekly 2018 retail scan data for National retail volume (units) and price. Retail scan data comes directly from retailers?? cash registers based on actual retail sales of Hass avocados. Starting in 2013, the table below reflects an expanded, multi-outlet retail data set. Multi-outlet reporting includes an aggregation of the following channels: grocery, mass, club, drug, dollar and military. The Average Price (of avocados) in the table reflects a per unit (per avocado) cost, even when multiple units (avocados) are sold in bags. The Product Lookup codes (PLU??s) in the table are only for Hass avocados. Other varieties of avocados (e.g. greenskins) are not included in this table.


#####Some relevant columns in the dataset

* Date - The date of the observation

* AveragePrice - the average price of a single avocado

* type - conventional or organic

* year - the year

* Region - the city or region of the observation

* Total Volume - Total number of avocados sold

* 4046 - Total number of avocados with PLU 4046 sold

* 4225 - Total number of avocados with PLU 4225 sold

* 4770 - Total number of avocados with PLU 4770 sold

[about PLU](http://indexfresh.com/retail-foodservice/brands/packaging/plus/)

>Data Analysis And Visualization

Do some element changes to organise materials in raw csv data

```{r warning=FALSE}
library(ggplot2)
library(RColorBrewer)
avocado = read.csv("avocado.csv")

avocado$year<-as.factor(avocado$year)
avocado$Date<-as.Date(avocado$Date)
avocado<-avocado[order(avocado$Date),]

str(avocado)
```


Compare the average price between two types of avocado in each year

```{r}
ggplot(avocado, aes(year, AveragePrice,colour = type)) +
  geom_boxplot()
```


Trend chart of avocado price

```{r}
ggplot(avocado, aes(Date, AveragePrice, colour = type)) +
  geom_point() +
  geom_smooth(color=brewer.pal(9, "BuPu")[5])

```


Distribution of average price and sales volume in three different PLU type

```{r}
ggplot(avocado, aes(AveragePrice, X4046)) +
  geom_point(color=brewer.pal(9, "YlGn")[4])

ggplot(avocado, aes(AveragePrice, X4225)) +
  geom_point(color=brewer.pal(9, "YlGn")[6])

ggplot(avocado, aes(AveragePrice, X4770)) +
  geom_point(color=brewer.pal(9, "YlGn")[8])
```
